Turbulence in compact to giant H~II regions

### 2023-04-23 strucfunc_paper.tex
Finish revision of first NGC 346 section

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. Diameters taken from Table 2 of \citet{1984ApJ...287..116K}. Mean non-thermal linewidth values (\(\langle \sigma\los \rangle\)) shown here are corrected considering equation \eqref{eq:sigma-los} which takes into account \(\sigma_{\mathrm{fs}}\). Non-corrected \(\langle \sigma\los \rangle\) values and other properties references are mentioned in the text. }
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ d & \text{Diameter,}\ D_{\hii} & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.44 \pm 0.02  & 5 \pm 0.5    &    37.18       &    9.9 \pm 1.2\FNa        \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   11.2 \pm 1.6    \\
Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    39.01    &   18.6 \pm 3.3\FNa      \\
30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &     21.7 \pm 2.2    \\
NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &    9.6 \pm 1.0     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   10.0 \pm 0.02\\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &    9.8 \pm 0.03     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   16.5 \pm 0.1     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   17.5 \pm 0.30     \\
\bottomrule
\multicolumn{5}{l}{\FNa{}Value obtained from our observations.}
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

@@

% START of revised material
\startNEW

\subsection{Orion Nebula}
\label{sec:orion-nebula}

The Orion Nebula (M42) is the prototype of a galactic \hii{} region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc}; \citealp{2008AJ....136.1566O}}.
The O7 V star \(\uptheta^{1}\) Ori C is the most luminous and hottest star with an ionizing flux \(Q_0\) of \SI{e49.12}{photons.s^{-1}} \citep{2006A&A...448..351S} which translates to luminosity in \ha{} of \SI{e37.18}{erg.s^{-1}}.
With other 3 B-type stars they form the Trapezium cluster.
The bright region that surrounds these massive ionizing stars is called the Huygens region.
%In the southwest direction of the Huygens region there is a drop in the brightness as one approach a much larger region called Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}
The position of the Orion Nebula on the near side of the Orion Molecular Cloud (OMC-1) makes it an ongoing site of star formation with a large population of young stars,
some of which are sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
Its physical properties and kinematics, along with its stellar population is documented in \citet{2001ARA&A..39...99O}.

\subsubsection{Observed structure function and model fit}
\label{sec:observ-struct-funct-orion}

@@

Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
A detailed description of the model fit is given in section~\ref{sec:example-results-orion} and will not be repeated here.
% The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{0.13}{pc} \),
% which corresponds to the total decorrelation length \(\tau_0\), see section~\ref{sec:comp-with-prev}). 
At scales larger than the correlation length,
a maximum \(B(r)\) value of \SI{23}{km^{2}.s^{-2}} is seen at \(r = \SI{0.30}{pc}\),
beyond which the structure function declines to \SI{7}{km^{2}.s^{-2}} at \(r =  \SI{0.5}{pc}\). 
This ``hook'' behavior can be explained by a radial gradient in the
amplitude of the velocity fluctuations (see section~\ref{sec:limit-model-struct}).

An alternative approach to determine the velocity variance and correlation length
is to empirically measure \(\sigma\pos^2\) from the observations and then to use linear
interpolation on the measured structure function to find the point where \(B(r_0) = \sigma\pos^2\).
This yields \(\sigma\pos^2 = \SI{9}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.05}{pc} \),
as compared to the model-derived values of \(\sigma\pos^2 = \SI{13}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.07}{pc} \).
The main reason for the discrepancy is the finite box effect
discussed in section~\ref{sec:finite-box-effects} above, where it is shown
that for homogeneous fluctuations it is necessary to sample a map of size \(L > 10 r_0\)
in order to empirically determine \(\sigma\pos^2\).
In the case of the Orion core observations, \(L = 7 r_0\),
so the fluctuations are not fully sampled, leading
to the empirical \(\sigma\pos^2\) being an underestimate.
However, given the evidence for a radial gradient in the amplitude of the velocity fluctuations,
it could be argued that the finite box effect is not so important as it would be for homogeneous fluctuations
and it is instead the model-derived value of \(\sigma\pos^2\) that is an overestimate.

@@

Figure~\ref{fig:strucfunc-fit-Galactic}b shows the structure function of the Extended Orion Nebula, which is ten times larger than the core in linear size,
but observed at a much lower angular resolution
(see Figures~\ref{fig:hii-regions} and~\ref{fig:velocity-maps}).
The data for this region are the lowest quality of all the regions in
our sample, and there are too many degeneracies between the parameters
to achieve a credible fit using the full model.
We therefore fix the power slope at \(m = 1\),
which implies that noise must make a significant contribution at all scales
in order to reproduce the observed flat structure function.
In turn, this implies that a true \(\sigma^2\pos = \SI{5}{km^2.s^{-2}}\),
which is lower than the \SI{7}{km^2.s^{-2}}
that would be naively derived from the observations
(compare green and orange lines in Figure~\ref{fig:strucfunc-fit-Galactic}b).
% The derived correlation length is \SI{0.5}{pc} which is above the \SI{0.3}{pc} required to determine the true correlation length but below the \SI{0.9}{pc} which guarantees that the fit can reliable determine \(r_0\).
Comparing the extended nebula with the core for the size scales where they overlap
(\num{0.1} to \SI{0.5}{pc}), one sees that \(B(r)\) is roughly four times smaller
in the EON than in the core for the same value of \(r\).
This is further evidence for a decline in the fluctuation amplitude with radius,
as mentioned above.
Also consistent with this is a hook-like downturn in \(B(r)\) for \(r > \SI{2}{pc}\)
for the EON region.
The fact that the derived \(r_0\) is larger for the EON region than the core
(\SI{0.5}{pc} versus \SI{0.07}{pc}) means that the correlation length is also inhomogeneous,
tending to increase from the center to the outskirts of the nebula.

%The seeing width is much smaller than the angular scale of the observations

\subsubsection{Comparison with previous studies}
\label{sec:comparison-orion}

\citet{arthur2016turbulence} calculated the structure function of different emission lines in the inner Orion Nebula with varying degrees of ionization. 
They found that higher ionization lines show a larger velocity dispersion
and a steeper structure function slope. 
They also make a comparison with previous work (see Table~5 on their paper), finding a broad agreement in results and the dependence between ionization energy and slope and dispersion value.
% The work by \citet{arthur2016turbulence} is the only one that includes the \ha{} emission line,
% for this reason it will be the only one that we use for comparison.
The power-law index obtained by \citet{arthur2016turbulence} is \(m \sim 1.17 \pm 0.08\) for \halpha,
% and [\ion{O}{3}] emission lines and for [\ion{S}{2}] and [\ion{N}{2}] they found \(m \sim 0.8 \pm 0.1\). 
with a correlation length of \SI{\sim 0.05}{pc} and velocity variance
\(\sigma\pos^2= \SI{9.4}{km^{2 }.s^{-2}}\).
This compares with our own values of
% For the same \halpha\ observations, but considering high-velocity objects, we obtained a value of 
\(m = 1.07 \pm 0.03\), \(r_0 = \SI{0.068 \pm 0.004}{pc}\)
and \(\sigma\pos^2 = \SI{13 \pm 1}{ km^{2}.s^{-2}}\). 
Since they are based on the same observational data,
the differences of order 30\% between the \citet{arthur2016turbulence}
results and our own are entirely due to the different methodologies employed.
In the case of \(\sigma\pos^2\), their value is lower than ours since
they masked out the locations of known high-velocity Herbig-Haro flows, whereas we do not.

\subsection{Lagoon Nebula}
\label{sec:lagoon-nebula}

The Lagoon Nebula (M8, NGC~6523) is located at a distance of \SI{1250}{pc}  \citetext{\SI{1}{\arcsecond} = \SI{0.006}{pc} ; \citealp{2005A&A...430..941P}}.
It contains the young stellar cluster NGC~6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9~Sgr, type O4V \citep{Damiani:2017b}.
The optically brightest part of the nebula is denoted the ``Hourglass nebula'',
which is illuminated by the O7 star Herschel~36 \citep{1986AJ.....91..870W}.
These stars gives an ionizing flux \(Q_0 = \SI{e49.41}{photons.s^{-1}}\) (2 times higher than in the Orion Nebula) and the luminosity in \ha{} is \SI{e37.47}{erg.s^{-1}} \citep{1984ApJ...287..116K}.
The mean non-thermal linewidth in \ha{} is \SI{11.7 \pm 1.6}{km.s^{-1}} \citep{1973ApJ...183..851B}.
Molecular gas and ongoing star formation are present in the region around
Herschel~36 \citep{Arias:2006e, Tiwari:2018a} and the lower-luminosity region
M8~East \citep{1984ApJ...278..170S, Tiwari:2020a}.
% The velocity field shows several expanding shells, related to the stellar population, and the massive protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation.
% A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister \hii{} regions \citep{Damiani:2017b}. 
The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.

\subsubsection{Observed structure function and model fit}
\label{sec:observ-struct-funct-lagoon}

% We follow the same procedure we use to describe the observed structure function of the Orion Nebula for the rest of the regions.
Figure~\ref{fig:strucfunc-fit-Galactic}c shows the structure function of the Lagoon nebula.
The model fit gives \(\sigma\pos^2 = \SI{7 \pm 1}{km^{2}.s^{-2}}\), \(r_0 = \SI{1 \pm 0.2}{pc} \), and \(m = 1.26 \pm 0.2\).
In this case, there is good agreement between the model value and empirical value of \(\sigma\pos^2\),
indicating that finite box effects are unimportant.
On the other hand, the model-derived \(m\) is steeper than would be naively derived
from the observations, which is a symptom of the effects  of noise.
At separations smaller than the correlation length, the structure function shows irregular oscillations about the mean ascending trend,
which are a symptom of the relatively small number of spatial points in this source.

At scales much larger than the correlation length
the structure function begins to increase again, reaching a value of \SI{66}{km^{2}.s^{-2}} at \SI{20}{pc},
which is greater than \(9 \sigma\pos^2\).
As discussed in section~\ref{sec:evid-inhom-at}, this may be a sign of periodicity
or a large-scale gradient in the velocity field.

% There aren't any points affected by the seeing (RMS) which has a value of \SI{0.01}{pc} (\(s_0\)=\SI{3.5}{\arcsecond}).
% If we consider the first point of this \(B(r)\) to be valid, which corresponds to \SI{0.55}{km^{2}.s^{-2}} at \(r = \SI{0.05}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{0.89} and \num{0.86}, respectively, while our derived value is \num{1.26}.

\subsubsection{Comparison with previous studies}
\label{sec:comparison-lagoon}
The first investigation of the Lagoon nebula structure function is from \citet{1970A&A.....8..486L},
who use Fabry-Perot observation of the \ha{} line to probe scales
between \SI{0.7}{pc} and \SI{7}{pc}.
They find a rising power-law behavior with slope of \(m = 0.64\),
which is slightly smaller than the value we derive.
However, given the very coarse binning in separation of their structure function,
and the fact that they do not account for noise or the flattening of the structure function at large scales,
their results are broadly consistent with ours,
with the value of \( \sigma\pos^2 = \SI{16}{km^{2}.s^{-2}}\) at \(r = \SI{3.5}{pc}\) being almost
identical to our own value at that scale.

@@

Another [\ion{O}{3}] \Wav{5007} study \citep{Chakraborty:1999a}
calculated the structure function in the Hourglass region of the nebula:
an area of \(\num{1} \times \SI{1}{arcmin^2}\) centered at Herschel~36.
As compared to the data used in this paper, which spans between \num{0.1} and \SI{10}{pc}),
their results cover smaller scales, between \num{0.012} and \SI{0.3}{pc}.
\citet{Chakraborty:1999a} report a rising power-law behavior with slope of \(m = 0.46\) over the entire range.
No flattening of the structure function at the largest scales was seen, but that is to be expected
if the correlation length is larger than the size of the region mapped.
The amplitude of the fluctuations is much higher (\(\sigma^2\pos = \SI{130}{km^2.s^{-2}}\)
than we find for the wider nebula (\(\sigma^2\pos = \SI{7}{km^2.s^{-2}}\)),
suggesting an even more extreme version of the inhomogeneity that we find in the Orion Nebula.
This is supported by the fact that the Hourglass region also shows
much larger line widths than the rest of the nebula \citep{Chakraborty:1999a},
which is probably a symptom of the ongoing active star formation in that region.

\subsection{Carina Nebula}
\label{sec:carina-nebula}

The Carina nebula is a large star-forming complex located at a distance of \SI{2 350}{pc} \citetext{\SI{1}{\arcsecond} = \SI{0.01}{pc}; \citealp{2006ApJ...644.1151S}}.
It contains young clusters like Trumpler~14 and~16, and Collinder~228 from the Car~OB1 association, one of the largest OB associations in the Galaxy.
This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet (WR) stars and the most luminous star is the blue variable $\eta$~Car.
The ionizing flux \(Q_0\) is \SI{e50.95}{photons.s^{-1}} \citep{2008hsf2.book..138S} (60 times higher compared to the Orion Nebula) and the luminosity in \ha{} of \SI{e39.01}{erg.s^{-1}}.
As a high-mass star formation region, it presents several phenomena related to young stars,
such as evaporating protoplanetary discs, erosion of large dust pillars, and the triggering of a second generation of embedded stars and Herbig-Haro objects \citetext{see \citealp{2008hsf2.book..138S} and reference therein}. 
This region is at an intermediate scale between nearby regions like Orion
that are dominated by a single star, and giant star formation regions such as 30~Doradus.

\subsubsection{Observed structure function and model fit}
\label{sec:observ-struct-funct-carina}

Figure~\ref{fig:strucfunc-fit-Galactic}d shows the structure function of the Carina nebula.
The model fit gives \(\sigma\pos^2 = \SI{18 \pm 2}{km^{2}.s^{-2}}\), \(r_0 = \SI{0.6 \pm 0.1}{pc} \), and \(m = 1.2 \pm 0.3\).
Again there is good agreement between the model value and empirically measured
value of \(\sigma\pos^2\),
indicating that finite box effects are unimportant. In addition, both noise and seeing are
found to be unimportant. 
Similarly to the Lagoon nebula,
the structure function of Carina also shows a non-uniform and irregular behavior
below the correlation length, which can again be ascribed to the sparse spatial sampling.
As a result of this, the power-law slope determination is not very precise.

On scales larger than the correlation length,
the structure function of the Carina nebula is remarkably flat
for \(r = 2\) to \SI{6}{pc},
in good agreement with the prediction of homogeneous fluctuations
(Figure~\ref{fig:model-strucfunc}a).
But at the largest scales accesible to our observations, there is evidence for low-amplitude
periodic fluctuations with a wavelength of \(\lambda \approx \SI{8}{pc}\),
which corresponds to the typical separation
between the individual star clusters that make up the complex
(for instance, between Tr~14 and Tr~16).

@@

\subsection{30 Doradus}
\label{sec:30-doradus}

The giant \hii{} region 30~Doradus (Tarantula Nebula) is located at a distance of \SI{49.9}{kpc} \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
The star cluster that energizes the region is NGC~2070, with a central core (known as R136)
with ionizing luminosity \(Q_0 = \SI{e51.40}{photons.s^{-1}}\)  \citep{2020MNRAS.499.1918B},
which produces an \ha{} luminosity of \SI{e39.46}{erg.s^{-1}} (200 times the Orion Nebula)
for the central ionized region of size \SI{40}{pc}.
The mean non-thermal linewidth in \ha{} is \SI{22}{km.s^{-1}} \citep{2013A&A...555A..60T}.
Star formation is still ongoing in NGC~2070 \citep{2013AJ....145...98W},
although the star-formation rate peaked about \SI{4}{Myr} ago
\citep{2015ApJ...811...76C} and it currently hosts some of the most massive stars known
\citep{Kalari:2022p}
and several Wolf-Rayet stars \citep{2011A&A...530A.108E}.
This nebula is commonly used as a comparison for extragalactic star-forming regions.

\subsubsection{Observed structure function and model fit}
\label{sec:observ-struct-funct-30dor}

>>>>

\begin{table}
  \begin{center}\caption{Summary of properties of our \hii{} region sample. Diameters are taken from Table 2 of \citet{1984ApJ...287..116K}.
      \NEW{References for other properties are given in Appendix~\ref{sec:notes-individual-hii}.}
      Mean non-thermal linewidth values (\(\langle \sigma\los \rangle\)) shown here are corrected considering equation \eqref{eq:sigma-los} which takes into account \(\sigma_{\mathrm{fs}}\). }
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ d & \text{Diameter,}\ D_{\hii} & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.44 \pm 0.02  & 5 \pm 0.5    &    37.18       &    9.9 \pm 1.2\FNa        \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   11.2 \pm 1.6    \\
Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    39.01    &   18.6 \pm 3.3\FNa      \\
30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &     21.7 \pm 2.2    \\
NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &    9.6 \pm 1.0     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   10.0 \pm 0.02\\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &    9.8 \pm 0.03     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   16.5 \pm 0.1     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   17.5 \pm 0.30     \\
\bottomrule
\multicolumn{5}{l}{\FNa{}Value obtained from our observations.}
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

@@

\startNEW
\subsection{Orion Nebula}
\label{sec:orion-nebula}
\stopNEW

The Orion Nebula (M42) is the prototype of a galactic \hii{} region located at a distance of 440 pc \citetext{\SI{1}{\arcsecond} = \SI{0.002}{pc}; \citealp{2008AJ....136.1566O}}.
The O7 V star \(\uptheta^{1}\) Ori C is the most luminous and hottest star with an ionizing flux \(Q_0\) of \SI{e49.12}{photons.s^{-1}} \citep{2006A&A...448..351S},
\startNEW
dominating the ionization of the nebula, which has a
\stopNEW
luminosity in \ha{} of \SI{e37.18}{erg.s^{-1}}.
With 3 other B-type stars they form the Trapezium cluster.
The bright region that surrounds these massive ionizing stars is called the Huygens region.
%In the southwest direction of the Huygens region there is a drop in the brightness as one approach a much larger region called Extended Orion Nebula \citetext{EON henceforth;  \citealp{2008Sci...319..309G}}
The position of the Orion Nebula \NEW{on the near side of} the Orion Molecular Cloud (OMC-1)
\startNEW
makes it an ongoing site of star formation with a large population of young stars,
\stopNEW
some of which are sources of stellar jets and Herbig-Haro objects \citep{1993ApJ...410..696O}.
Its physical properties and kinematics, along with its stellar population is documented in \citet{2001ARA&A..39...99O}.

\startNEW
\subsubsection{Observed structure function and model fit}
\label{sec:observ-struct-funct-orion}
\stopNEW

@@

Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
A detailed description of the model fit is given in section~\ref{sec:example-results-orion} and will not be repeated here.
% The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{0.13}{pc} \),
% which corresponds to the total decorrelation length \(\tau_0\), see section~\ref{sec:comp-with-prev}).
\startNEW
At scales larger than the correlation length,
a maximum \(B(r)\) value of \SI{23}{km^{2}.s^{-2}} is seen at \(r = \SI{0.30}{pc}\),
beyond which the structure function declines to \SI{7}{km^{2}.s^{-2}} at \(r =  \SI{0.5}{pc}\). 
This ``hook'' behavior can be explained by a radial gradient in the
amplitude of the velocity fluctuations (see section~\ref{sec:limit-model-struct}).

An alternative approach to determine the velocity variance and correlation length
is to empirically measure \(\sigma\pos^2\) from the observations and then to use linear
interpolation on the measured structure function to find the point where \(B(r_0) = \sigma\pos^2\).
This yields \(\sigma\pos^2 = \SI{9}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.05}{pc} \),
as compared to the model-derived values of \(\sigma\pos^2 = \SI{13}{km^{2}.s^{-2}}\) and \(r_0 = \SI{0.07}{pc} \).
The main reason for the discrepancy is the finite box effect
discussed in section~\ref{sec:finite-box-effects} above, where it is shown
that for homogeneous fluctuations it is necessary to sample a map of size \(L > 10 r_0\)
in order to empirically determine \(\sigma\pos^2\).
In the case of the Orion core observations, \(L = 7 r_0\),
so the fluctuations are not fully sampled, leading
to the empirical \(\sigma\pos^2\) being an underestimate.
However, given the evidence for a radial gradient in the amplitude of the velocity fluctuations,
it could be argued that the finite box effect is not so important as it would be for homogeneous fluctuations
and it is instead the model-derived value of \(\sigma\pos^2\) that is an overestimate.
\stopNEW

@@

Figure~\ref{fig:strucfunc-fit-Galactic}b shows the structure function of the Extended Orion Nebula, which is ten times larger than the core in linear size,
but observed at a much lower angular resolution
(see Figures~\ref{fig:hii-regions} and~\ref{fig:velocity-maps}).
The data for this region are the lowest quality of all the regions in
our sample, and there are too many degeneracies between the parameters
to achieve a credible fit using the full model.
We therefore fix the power slope at \(m = 1\),
which implies that noise must make a significant contribution at all scales
in order to reproduce the observed flat structure function.
In turn, this implies that
\startNEW
the true velocity variance is
\stopNEW
\(\sigma^2\pos = \SI{5}{km^2.s^{-2}}\),
which is lower than the \SI{7}{km^2.s^{-2}}
that would be naively derived from the observations
(compare green and orange lines in Figure~\ref{fig:strucfunc-fit-Galactic}b).
% The derived correlation length is \SI{0.5}{pc} which is above the \SI{0.3}{pc} required to determine the true correlation length but below the \SI{0.9}{pc} which guarantees that the fit can reliable determine \(r_0\).
\startNEW
Comparing the extended nebula with the core for the size scales where they overlap
(\num{0.1} to \SI{0.5}{pc}), one sees that \(B(r)\) is roughly four times smaller
in the EON than in the core for the same value of \(r\).
This is further evidence for a decline in the fluctuation amplitude with radius,
as mentioned above.
Also consistent with this is a hook-like downturn in \(B(r)\) for \(r > \SI{2}{pc}\)
for the EON region.
The fact that the derived \(r_0\) is larger for the EON region than the core
(\SI{0.5}{pc} versus \SI{0.07}{pc}) means that the correlation length is also inhomogeneous,
tending to increase from the center to the outskirts of the nebula. 
\stopNEW

%The seeing width is much smaller than the angular scale of the observations
\startNEW
\subsubsection{Comparison with previous studies}
\label{sec:comparison-orion}
\stopNEW

\citet{arthur2016turbulence}
\startNEW
calculated the structure function of different emission lines in the inner Orion Nebula with varying degrees of ionization.
They found that higher ionization lines show a larger velocity dispersion
and a steeper structure function slope.
\stopNEW
They also make a comparison with previous work (see Table~5 of their paper), finding a broad
\startNEW
agreement in derived structure function parameters
and their dependence on ionization energy.
\stopNEW
% The work by \citet{arthur2016turbulence} is the only one that includes the \ha{} emission line,
% for this reason it will be the only one that we use for comparison.
The power-law index obtained by \citet{arthur2016turbulence} is
\startNEW
\(m \sim 1.17 \pm 0.08\) for \halpha,
with a correlation length of \SI{\sim 0.05}{pc} and velocity variance
\(\sigma\pos^2= \SI{9.4}{km^{2 }.s^{-2}}\).
This compares with our own values of
\(m = 1.07 \pm 0.03\), \(r_0 = \SI{0.068 \pm 0.004}{pc}\)
and \(\sigma\pos^2 = \SI{13 \pm 1}{ km^{2}.s^{-2}}\). 
Since they are based on the same observational data,
the differences of order 30\% between the \citet{arthur2016turbulence}
results and our own are entirely due to the different methodologies employed.
In the case of \(\sigma\pos^2\), their value is lower than ours since
they masked out the locations of known high-velocity Herbig-Haro flows, whereas we do not.
\stopNEW

\startNEW
\subsection{Lagoon Nebula}
\label{sec:lagoon-nebula}
\stopNEW

The Lagoon Nebula (M8, NGC~6523) is located at a distance of \SI{1250}{pc}  \citetext{\SI{1}{\arcsecond} = \SI{0.006}{pc} ; \citealp{2005A&A...430..941P}}.
It contains the young stellar cluster NGC~6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9~Sgr, type O4V \citep{Damiani:2017b}.
\startNEW
The optically brightest part of the nebula is denoted the ``Hourglass nebula'',
which is illuminated by the O7 star Herschel~36 \citep{1986AJ.....91..870W}.
\stopNEW
These stars gives an ionizing flux \(Q_0 = \SI{e49.41}{photons.s^{-1}}\) (2 times higher than in the Orion Nebula) and the luminosity in \ha{} is \SI{e37.47}{erg.s^{-1}} \citep{1984ApJ...287..116K}.
The mean non-thermal linewidth in \ha{} is \SI{11.7 \pm 1.6}{km.s^{-1}} \citep{1973ApJ...183..851B}.
\startNEW
Molecular gas and ongoing star formation are present in the region around
Herschel~36 \citep{Arias:2006e, Tiwari:2018a} and the lower-luminosity region
M8~East \citep{1984ApJ...278..170S, Tiwari:2020a}.
\stopNEW
The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.

\startNEW
\subsubsection{Observed structure function and model fit}
\label{sec:observ-struct-funct-lagoon}

Figure~\ref{fig:strucfunc-fit-Galactic}c shows the structure function of the Lagoon nebula.
The model fit gives \(\sigma\pos^2 = \SI{7 \pm 1}{km^{2}.s^{-2}}\), \(r_0 = \SI{1 \pm 0.2}{pc} \), and \(m = 1.26 \pm 0.2\).
In this case, there is good agreement between the model value and empirical value of \(\sigma\pos^2\),
indicating that finite box effects are unimportant.
On the other hand, the model-derived \(m\) is steeper than would be naively derived
from the observations, which is a symptom of the effects  of noise.
At separations smaller than the correlation length, the structure function shows irregular oscillations about the mean ascending trend,
which are a symptom of the relatively small number of spatial points in this source.

At scales much larger than the correlation length
the structure function begins to increase again, reaching a value of \SI{66}{km^{2}.s^{-2}} at \SI{20}{pc},
which is greater than \(9 \sigma\pos^2\).
As discussed in section~\ref{sec:evid-inhom-at}, this may be a sign of periodicity
or a large-scale gradient in the velocity field.
\stopNEW

\startNEW
\subsubsection{Comparison with previous studies}
\label{sec:comparison-lagoon}
The first investigation of the Lagoon nebula structure function is from \citet{1970A&A.....8..486L},
who use Fabry-Perot observation of the \ha{} line to probe scales
between \SI{0.7}{pc} and \SI{7}{pc}.
They find a rising power-law behavior with slope of \(m = 0.64\),
which is slightly smaller than the value we derive.
However, given the very coarse binning in separation of their structure function,
and the fact that they do not account for noise or the flattening of the structure function at large scales,
their results are broadly consistent with ours,
with the value of \( \sigma\pos^2 = \SI{16}{km^{2}.s^{-2}}\) at \(r = \SI{3.5}{pc}\) being almost
identical to our own value at that scale.

@@

Another [\ion{O}{3}] \Wav{5007} study \citep{Chakraborty:1999a}
calculated the structure function in the Hourglass region of the nebula:
an area of \(\num{1} \times \SI{1}{arcmin^2}\) centered at Herschel~36.
As compared to the data used in this paper, which spans between \num{0.1} and \SI{10}{pc}),
their results cover smaller scales, between \num{0.012} and \SI{0.3}{pc}.
\citet{Chakraborty:1999a} report a rising power-law behavior with slope of \(m = 0.46\) over the entire range.
No flattening of the structure function at the largest scales was seen, but that is to be expected
if the correlation length is larger than the size of the region mapped.
The amplitude of the fluctuations is much higher (\(\sigma^2\pos = \SI{130}{km^2.s^{-2}}\))
than we find for the wider nebula (\(\sigma^2\pos = \SI{7}{km^2.s^{-2}}\)),
suggesting an even more extreme version of the inhomogeneity that we find in the Orion Nebula.
This is supported by the fact that the Hourglass region also shows
much larger line widths than the rest of the nebula \citep{Chakraborty:1999a},
which is probably a symptom of the ongoing active star formation in that region.
\stopNEW

\startNEW
\subsection{Carina Nebula}
\label{sec:carina-nebula}
\stopNEW

The Carina nebula is a large star-forming complex located at a distance of \SI{2 350}{pc} \citetext{\SI{1}{\arcsecond} = \SI{0.01}{pc}; \citealp{2006ApJ...644.1151S}}.
It contains young clusters like Trumpler~14 and~16, and Collinder~228 from the Car~OB1 association, one of the largest OB associations in the Galaxy.
This OB association has more than 65 stars earlier than B0, and several Wolf-Rayet (WR) stars and the most luminous star is the blue variable $\eta$~Car.
The ionizing flux \(Q_0\) is \SI{e50.95}{photons.s^{-1}} \citep{2008hsf2.book..138S} (60 times higher compared to the Orion Nebula) and the luminosity in \ha{} of \SI{e39.01}{erg.s^{-1}}.
As a high-mass star formation region, it presents several phenomena related to young stars,
such as evaporating protoplanetary discs, erosion of large dust pillars, and the triggering of a second generation of embedded stars and Herbig-Haro objects \citetext{see \citealp{2008hsf2.book..138S} and reference therein}.
\startNEW
This region is at an intermediate scale between nearby regions like Orion
that are dominated by a single star, and giant star formation regions such as 30~Doradus.
\stopNEW

\startNEW
\subsubsection{Observed structure function and model fit}
\label{sec:observ-struct-funct-carina}
\stopNEW

Figure~\ref{fig:strucfunc-fit-Galactic}d shows the structure function of the Carina nebula.
\startNEW
The model fit gives \(\sigma\pos^2 = \SI{18 \pm 2}{km^{2}.s^{-2}}\), \(r_0 = \SI{0.6 \pm 0.1}{pc} \), and \(m = 1.2 \pm 0.3\).
Again there is good agreement between the model value and empirically measured
value of \(\sigma\pos^2\),
indicating that finite box effects are unimportant. In addition, both noise and seeing are
found to be unimportant. 
Similarly to the Lagoon nebula,
the structure function of Carina also shows a non-uniform and irregular behavior
below the correlation length, which can again be ascribed to the sparse spatial sampling.
As a result of this, the power-law slope determination is not very precise.

On scales larger than the correlation length,
the structure function of the Carina nebula is remarkably flat
for \(r = 2\) to \SI{6}{pc},
in good agreement with the prediction of homogeneous fluctuations
(Figure~\ref{fig:model-strucfunc}a).
But at the largest scales accesible to our observations, there is evidence for low-amplitude
periodic fluctuations with a wavelength of \(\lambda \approx \SI{8}{pc}\),
which corresponds to the typical separation
between the individual star clusters that make up the complex
(for instance, between Tr~14 and Tr~16).
\stopNEW

@@

\startNEW
\subsection{30 Doradus}
\label{sec:30-doradus}
\stopNEW

The giant \hii{} region 30~Doradus (Tarantula Nebula) is located at a distance of \SI{49.9}{kpc} \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc}; \citealp{2013Natur.495...76P}}.
It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
\startNEW
The star cluster that energizes the region is NGC~2070, with a central core (known as R136)
with ionizing luminosity \(Q_0 = \SI{e51.40}{photons.s^{-1}}\)  \citep{2020MNRAS.499.1918B},
which produces an \ha{} luminosity of \SI{e39.46}{erg.s^{-1}} (200 times the Orion Nebula)
for the central ionized region of size \SI{40}{pc}.
\stopNEW
The mean non-thermal linewidth in \ha{} is \SI{22}{km.s^{-1}} \citep{2013A&A...555A..60T}.
\startNEW
Star formation is still ongoing in NGC~2070 \citep{2013AJ....145...98W},
although the star-formation rate peaked about \SI{4}{Myr} ago
\citep{2015ApJ...811...76C} and it currently hosts some of the most massive stars known
\citep{Kalari:2022p}
and several Wolf-Rayet stars \citep{2011A&A...530A.108E}.
\stopNEW
This nebula is commonly used as a comparison for extragalactic star-forming regions.

\startNEW
\subsubsection{Observed structure function and model fit}
\label{sec:observ-struct-funct-30dor}
